Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2020-12-04 manuscript.tex
Update front matter [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/eb8aa2674994b5d0a1520095ebc7a0cda2545638.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/eb8aa2674994b5d0a1520095ebc7a0cda2545638/checks
https://github.com/habi/acinar-analysis-manuscript/runs/401121064

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/786681} and has been submitted to the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}.
This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...b6c94bd9b09a75063c29a39afcb8831a1724e180}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/b6c94bd9b09a75063c29a39afcb8831a1724e180/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/b6c94bd9b09a75063c29a39afcb8831a1724e180}{habi/acinar-analysis-manuscript@b6c94bd}
on December 4, 2020.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Switzerland
  · Funded by Swiss National Science Foundation grants \href{http://p3.snf.ch/project-153468}{310030\_153468} and \href{http://p3.snf.ch/project-175953}{310030\_175953}
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Switzerland
  · Funded by Swiss National Science Foundation grants \href{http://p3.snf.ch/project-153468}{310030\_153468} and \href{http://p3.snf.ch/project-175953}{310030\_175953}
\item
  \textbf{Tiziana P. Cremona}
  \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Switzerland
  · Funded by Swiss National Science Foundation grants \href{http://p3.snf.ch/project-153468}{310030\_153468} and \href{http://p3.snf.ch/project-175953}{310030\_175953}
\item
  \textbf{Stefan A. Tschanz}
  \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}
  \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  Institute of Anatomy, University of Bern, Switzerland
  · Funded by Swiss National Science Foundation grants \href{http://p3.snf.ch/project-153468}{310030\_153468} and \href{http://p3.snf.ch/project-175953}{310030\_175953}; Swiss National Science Foundation grants \href{http://p3.snf.ch/project-153468}{310030\_153468} and \href{http://p3.snf.ch/project-175953}{310030\_175953}
\end{itemize}

✉: Corresponding author. Correspondence preferred via \href{https://github.com/habi/acinar-analysis-manuscript/issues}{GitHub Issues}.

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/786681} and has been submitted to the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}.

This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...eb8aa2674994b5d0a1520095ebc7a0cda2545638}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/eb8aa2674994b5d0a1520095ebc7a0cda2545638/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/eb8aa2674994b5d0a1520095ebc7a0cda2545638}{habi/acinar-analysis-manuscript@eb8aa26}
on December 4, 2020.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  Institute of Anatomy, University of Bern, Switzerland
\end{itemize}

✉: Corresponding author. Correspondence preferred via \href{https://github.com/habi/acinar-analysis-manuscript/issues}{GitHub Issues}, though.
